ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-12 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

{\bf Performance.} MPOR resulted in a performance improvement of approximately $80\%$, by decreasing the verification time from $16$ to $3$ hours, while the two-threads analysis further reduced that to $789.6$ sec. Although such techniques have considerably improved the ESBMC-GPU's performance, it still takes longer than the other evaluated tools: GPUVerify ($98.36$ sec), GKLEE ($108.32$ sec), and CIVL ($708.52$ sec). This is due to thread interleavings, which combine symbolic model checking with explicit state-space exploration~\cite{pereira:2016}. %In addition, even though ESBMC-GPU reports the highest verification time, it still presents the highest accuracy, with less than $6$ seconds per benchmark.%, which shows that it is a feasible tool regarding the verification of CUDA-based applications. 
\textcolor{blue}{On the other hand}, ESBMC-GPU still presents the highest accuracy, with less than $6$ seconds per benchmark.

>>>>

{\bf Performance.} MPOR resulted in a performance improvement of approximately $80\%$, by decreasing the verification time from $16$ to $3$ hours, while the two-threads analysis further reduced that to $789.6$ sec. Although such techniques have considerably improved the ESBMC-GPU's performance, it still takes longer than the other evaluated tools: GPUVerify ($98.36$ sec), GKLEE ($108.32$ sec), and CIVL ($708.52$ sec). \textcolor{blue}{On the one hand}, this is due to thread interleavings, which combine symbolic model checking with explicit state-space exploration~\cite{pereira:2016}. %In addition, even though ESBMC-GPU reports the highest verification time, it still presents the highest accuracy, with less than $6$ seconds per benchmark.%, which shows that it is a feasible tool regarding the verification of CUDA-based applications. 
\textcolor{blue}{On the other hand}, ESBMC-GPU still presents the highest accuracy, with less than $6$ seconds per benchmark.
